Stack Safety as a Security Property

### 2020-07-04 main.tex
Committing to be able to pull; working on examples

\input{macros}

@@

\setcounter{pcctr}{27}
% H - Body
\vspace*{0.2em}
\[
\begin{array}{c|c|c|c|c}
  \row{\lw ~ r_4 ~ \rsp ~ 0}{r_4 \leftarrow [\rsp]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[105] \leftarrow 18}
      {Set {\tt w} to 18}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 106}
      {Deallocate {\tt h}'s call frame}
  \row{\lw ~ r_5 ~ \rsp ~ \negate 6}{r_5 \leftarrow [\rsp - 6]}{r_5 \leftarrow 0}
      {Load argument {\tt z} $r_5$}
  \row{\sw ~ \rout ~ r_5 ~ 0}{[\rout] \leftarrow r_5}{[99] \leftarrow 0}
      {Print {\tt z}}      
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 18}
      {Add $r_4$ and $r_5$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[103] \leftarrow 18}
      {Store $r_4$ as ther return of {\tt g}}
  \row{\lw ~ \rra ~ \rsp ~ \negate 2}{\rra \leftarrow [\rsp - 2]}{\rra \leftarrow 8}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 104}
      {Deallocate {\tt g}'s local state}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 8}{Return to {\tt main}}
\end{array}
\]
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{green}[{\makebox[0pt]{${\texttt main}_{priv}$}}]%
\memory{2}{green}[{\makebox[0pt]{{\tt g}'s call frame }}]%
\memory{6}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{0}
\MemoryLabel{-47em}{0.75em}{42}
\MemoryLabel{-43em}{0.75em}{0}
\MemoryLabel{-39em}{0.75em}{0}
\MemoryLabel{-35em}{0.75em}{18}
\\
\end{center}
% Register File
\summary{8}{0}{\thepcctr}{104}{18}{0}
%\vspace*{0.2em}
\setcounter{pcctr}{8}
\[
\begin{array}{c|c|c|c|c}
  \row{\lw ~ \rsp ~ r_4 ~ \negate 1}{r_4 \leftarrow [\rsp - 1]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[101] \leftarrow 18}
      {Set {\tt y} to the result}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 4}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 102}
      {Deallocate {\tt g}'s call frame}
  \row{\lw ~ \rsp ~ r_5 ~ \negate 2}{r_5 \leftarrow [\rsp - 2]}{r_5 \leftarrow 42}
      {Load {\tt x} to $r_5$}
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 60}
      {Add {\tt x} and {\tt y}}
  \row{\sw ~ \rout ~ r_4 ~ 0}{[\rout] \leftarrow r_4}{[99] \leftarrow 60}
      {Print {\tt x + y}}
\end{array}
\]
\vspace*{0.2em}
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{31.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{green}[{\makebox[0pt]{${\texttt main}_{priv}$}}]%
\memory{8}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{60}
\MemoryLabel{-47em}{0.75em}{60}
\MemoryLabel{-43em}{0.75em}{42}
\\
\end{center}
% Starting Register File
\summary{\thepcctr}{0}{37}{102}{60}{42}
\caption{Detailed Execution Trace}
\label{fig:running-trace-b}
\end{figure}

@@

\begin{figure}
% At Call to H
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
  \memory{6}{red}[{\makebox[0pt]{\(\HIGHINT\)}}]%
  \memory{2}{green}[{\makebox[0pt]{\(\LOWINT\)}}]%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\\
\end{center}
% Starting Register File
\summary{40}{0}{\thepcctr}{108}{17}{?}
\setcounter{pcctr}{40}
\vspace*{0.2em}
% H - Body
\[
\begin{array}{c|c|c|c|c}
  \row{\addi ~ \rsp ~ \rsp ~ 1}{\rsp \leftarrow \rsp + 1}{\rsp \leftarrow 109}
      {Allocate for return address}
  \row{\sw ~ \rsp ~ \rra ~ \negate 1}{[\rsp - 1] \leftarrow \rra}{[108] \leftarrow 27}
      {Store return address}
  \row{\lw ~ r_4 ~ \rsp ~ \negate 3}{r_4 \leftarrow [\rsp - 3]}{r_4 \leftarrow 17}
      {Load the argument {\tt v} to $r_4$}
  \row{\addi ~ r_4 ~ r_4 ~ 1}{r_4 \leftarrow r_4 + 1}{r_4 \leftarrow 18}
      {Increment $r_4$ by 1}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 5}{[\rsp - 5] \leftarrow r_4}{[103] \leftarrow 18}
      {Store $r_4$ as {\tt g}'s return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\rra \leftarrow 31}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 1}{\rsp \leftarrow \rsp - 1}{\rsp \leftarrow 108}
      {Restore the stack pointer of {\tt g}}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 31}
      {Return to {\tt g}}
  \end{array}
\]
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{44em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
  \memory{3}{red}%
  \memory{1}{green}%
  \memory{2}{red}%
  \memory{2}{gray}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{18}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\MemoryLabel{-16em}{0.75em}{108}
\\
\end{center}
%
  \caption{Failing Trace Integrity}
  \label{fig:intex}
\end{figure}

\begin{figure}
% At Call to H
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
  \memory{6}{red}[{\makebox[0pt]{\(\HIGHSEC\)}}]%
  \memory{2}{green}[{\makebox[0pt]{\(\LOWSEC\)}}]%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\\
\end{center}
% Variant
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{61.5em}{2em}{\SP}
\memory{3}{gray}%
\hspace*{3pt}
$\cdots$
\memory{1}{white}%
  \memory{6}{yellow}[{\makebox[0pt]{Varied}}]%
  \memory{2}{green}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{?}
\MemoryLabel{-42.5em}{0.75em}{?}
\MemoryLabel{-38.5em}{0.75em}{?}
\MemoryLabel{-34.5em}{0.75em}{?}
\MemoryLabel{-30.5em}{0.75em}{?}
\MemoryLabel{-26.5em}{0.75em}{?}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-18.5em}{0.75em}{0}
\\
\end{center}

% Starting Register File
\summary{40}{0}{\thepcctr}{108}{17}{?}
\setcounter{pcctr}{40}
\vspace*{0.2em}
% H - Body
\[
\begin{array}{c|c|c|c|c}
  \row{\addi ~ \rsp ~ \rsp ~ 1}{\rsp \leftarrow \rsp + 1}{\rsp \leftarrow 109}
      {Allocate for return address}
  \row{\sw ~ \rsp ~ \rra ~ \negate 1}{[\rsp - 1] \leftarrow \rra}{[108] \leftarrow 27}
      {Store return address}
  \row{\lw ~ r_4 ~ 100}{r_4 \leftarrow 100}{r_4 \leftarrow 42/?}
      {Load {\tt main}'s secret {\tt x} to $r_4$}
  \row{\addi ~ r_4 ~ r_4 ~ 1}{r_4 \leftarrow r_4 + 1}{r_4 \leftarrow 43/(?+1)}
      {Increment $r_4$ by 1}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 2}{[\rsp - 2] \leftarrow r_4}{[107] \leftarrow 43/(?+1)}
      {Store $r_4$ as the return value}
  \row{\lw ~ \rra ~ \rsp ~ \negate 1}{\rra \leftarrow [\rsp - 1]}{\rra \leftarrow 31}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 1}{\rsp \leftarrow \rsp - 1}{\rsp \leftarrow 108}
      {Restore the stack pointer of {\tt g}}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 31}
      {Return to {\tt g}}
  \end{array}
\]
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{44em}{2em}{\SP}
\memory{3}{gray}%
\hspace*{3pt}
$\cdots$
\memory{1}{white}%
  \memory{6}{red}%
  \memory{1}{green}%
  \memory{1}{pink}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{42}
\MemoryLabel{-42.5em}{0.75em}{0}
\MemoryLabel{-38.5em}{0.75em}{0}
\MemoryLabel{-34.5em}{0.75em}{0}
\MemoryLabel{-30.5em}{0.75em}{8}
\MemoryLabel{-26.5em}{0.75em}{}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-19em}{0.75em}{43}
\MemoryLabel{-16em}{0.75em}{108}
\\
\end{center}
%
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{44em}{2em}{\SP}
\memory{3}{gray}%
\hspace*{3pt}
$\cdots$
\memory{1}{white}%
  \memory{6}{yellow}%
  \memory{1}{green}%
  \memory{1}{pink}%
\memory{2}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-46.5em}{0.75em}{?}
\MemoryLabel{-42.5em}{0.75em}{?}
\MemoryLabel{-38.5em}{0.75em}{?}
\MemoryLabel{-34.5em}{0.75em}{?}
\MemoryLabel{-30.5em}{0.75em}{?}
\MemoryLabel{-26.5em}{0.75em}{?}
\MemoryLabel{-22.5em}{0.75em}{17}
\MemoryLabel{-19em}{0.75em}{?}
\MemoryLabel{-16em}{0.75em}{108}
\\
\end{center}
%
  \caption{Failing Trace Confidentiality}
  \label{fig:confex2}
\end{figure}

>>>>

\input{macros}
\input{examples}

@@

\setcounter{pcctr}{27}
% H - Body
\vspace*{0.2em}
\[
\begin{array}{c|c|c|c|c}
  \row{\lw ~ r_4 ~ \rsp ~ 0}{r_4 \leftarrow [\rsp]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[105] \leftarrow 18}
      {Set {\tt w} to 18}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 106}
      {Deallocate {\tt h}'s call frame}
  \row{\lw ~ r_5 ~ \rsp ~ \negate 4}{r_5 \leftarrow [\rsp - 4]}{r_5 \leftarrow 0}
      {Load argument {\tt z} $r_5$}
  \row{\sw ~ \rout ~ r_5 ~ 0}{[\rout] \leftarrow r_5}{[99] \leftarrow 0}
      {Print {\tt z}}      
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 18}
      {Add $r_4$ and $r_5$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[103] \leftarrow 18}
      {Store $r_4$ as ther return of {\tt g}}
  \row{\lw ~ \rra ~ \rsp ~ \negate 2}{\rra \leftarrow [\rsp - 2]}{\rra \leftarrow 8}
      {Load return address}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 2}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 104}
      {Deallocate {\tt g}'s local state}
  \row{\jalr ~ \rra ~ \rra ~ 0}{??}{PC \leftarrow 8}{Return to {\tt main}}
\end{array}
\]
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{43.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{green}[{\makebox[0pt]{${\texttt main}_{priv}$}}]%
\memory{2}{green}[{\makebox[0pt]{{\tt g}'s call frame }}]%
\memory{6}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{0}
\MemoryLabel{-47em}{0.75em}{42}
\MemoryLabel{-43em}{0.75em}{0}
\MemoryLabel{-39em}{0.75em}{0}
\MemoryLabel{-35em}{0.75em}{18}
\\
\end{center}
% Register File
\summary{8}{0}{\thepcctr}{104}{18}{0}
%\vspace*{0.2em}
\setcounter{pcctr}{8}
\[
\begin{array}{c|c|c|c|c}
  \row{\lw ~ \rsp ~ r_4 ~ \negate 1}{r_4 \leftarrow [\rsp - 1]}{r_4 \leftarrow 18}
      {Load return value to $r_4$}
  \row{\sw ~ \rsp ~ r_4 ~ \negate 3}{[\rsp - 3] \leftarrow r_4}{[101] \leftarrow 18}
      {Set {\tt y} to the result}
  \row{\addi ~ \rsp ~ \rsp ~ \negate 4}{\rsp \leftarrow \rsp - 2}{\rsp \leftarrow 102}
      {Deallocate {\tt g}'s call frame}
  \row{\lw ~ \rsp ~ r_5 ~ \negate 2}{r_5 \leftarrow [\rsp - 2]}{r_5 \leftarrow 42}
      {Load {\tt x} to $r_5$}
  \row{\add ~ r_4 ~ r_4 ~ r_5}{r_4 \leftarrow r_4 + r_5}{r_4 \leftarrow 60}
      {Add {\tt x} and {\tt y}}
  \row{\sw ~ \rout ~ r_4 ~ 0}{[\rout] \leftarrow r_4}{[99] \leftarrow 60}
      {Print {\tt x + y}}
\end{array}
\]
\vspace*{0.2em}
% Return to main
% Memory Layout
\begin{center}
\MemoryLabel{4em}{2em}{0}
\MemoryLabel{21em}{2em}{99}
\MemoryLabel{31.5em}{2em}{\SP}
\memory{3}{gray}[{\makebox[0pt]{Instructions}}]%
\hspace*{3pt}
$\cdots$
\memory{1}{white}[{\makebox[0pt]{Output}}]%
\memory{2}{green}[{\makebox[0pt]{${\texttt main}_{priv}$}}]%
\memory{8}{gray}%[{\makebox[0pt]{Uninitialized}}]
~$\cdots$
\MemoryLabel{-51em}{0.75em}{60}
\MemoryLabel{-47em}{0.75em}{60}
\MemoryLabel{-43em}{0.75em}{42}
\\
\end{center}
% Starting Register File
\summary{\thepcctr}{0}{37}{102}{60}{42}
\caption{Detailed Execution Trace
  \rb{A suggestion for the description of $\jal$ and $\jalr$:
    call(function label) [if labels are added next to the entrypoints]
    or call(address of entrypoint) and return()?}
}
\label{fig:running-trace-b}
\end{figure}

@@

\begin{figure}
  \integrityexample
  \caption{Failing Trace Integrity}
  \label{fig:intex}
\end{figure}

\begin{figure}
  \integritylazyexample
  \caption{Rolling back from Figure \ref{fig:intex}}
  \label{fig:intlex}
\end{figure}

\begin{figure}
  \confidentialityduringexample
  \caption{Failing Trace Confidentiality by Varying Observations}
  \label{fig:confex1}
\end{figure}

\begin{figure}
  \confidentialityendexample
  \caption{Failing Trace Confidentiality at End State}
  \label{fig:confex2}
\end{figure}
